Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-10 manuscript/main.tex
changed supp table reference
updated brain importance numbers

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|}
      \hline\hline
      \textbf{Statistic} & \textbf{MAPE} & \textbf{R} \\\hline
      Mean & 0.069 & 0.206 \\
      Standard deviation & 0.015 & 0.099 \\
      Maximum & 0.11 & 0.444 \\
      75th percentile & 0.076 & 0.262 \\
      50th percentile & 0.066 & 0.206 \\
      25th percentile & 0.057 & 0.16 \\
      Minimum & 0.046 & 0.005 \\\hline
    \end{tabular}
    \caption{\label{tab:neuro}Summary statistics for the neuroanatomy prediction benchmarks.
    Mean absolute proportional error (MAPE) and correlation coeficient (R)
    of test-set preditions are reported accross models for all brain regions.
    Complete list of values can be found on Table S2.}
    \end{center}
\end{table}

@@

Among these, \emph{A. hadrus} is the variable with 
highest average relative importance along all reported 
(mean = 1.7\%; min = 1.0\%; max = 3.8\%, Figure 4D-E).
\emph{B. wexlerae}, which was important in RF models of cognitive function,
and was the only species to be significantly associated
with cogntive function in young children using LMs, 
was also important in models of the entorhinal, fusiform and lingual areas
and had the highest importance in models predicting the size of
both the left and right right parahippocampus.
Another cluster of model importance contained taxa associated with the
basal forebrain, especially the cingulate and the accumbens. This
cluster contains \emph{B. ovatus} and \emph{B. uniformis},
but also \emph{Alistipes finegoldii and S. salivarius}.

\emph{A. celatus}, an equol-producing species, is an examples of the second contribution
pattern, where a taxon only contributes significantly to a very small number of segments. 
This species was highly important in predicting the relative volume of
the right anterior cingulate (respectively, \hl{3.0\% and 2.6\%} importances).
Another example of this pattern is \emph{Coprococcus eutactus}
which is heavily associated with the left precentral area (\hl{2.7\%} importance). 
Finally, \emph{C. comes} has an importance
distribution that splits almost evenly among the two previously reported
clusters. Its loading on the prediction of the left posterior cingulate
is the highest for a microbe in RF models (\hl{4.0\%} importance);
only age had higher relative importance in any model. At the same time,
\textit{C. comes} is one of the most important predictors for neighboring areas of the
posterior cingulate such as the pars opercularis (importances,
\hl{Left = 2.3\%, Right = 2.8\%}), along with upper regions like the left
precentral (2.3\% importance) and paracentral lobes (importances, \hl{Left = 2.6\%, Right = 1.9\%}).

>>>>

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|}
      \hline\hline
      \textbf{Statistic} & \textbf{MAPE} & \textbf{R} \\\hline
      Mean & 0.069 & 0.206 \\
      Standard deviation & 0.015 & 0.099 \\
      Maximum & 0.11 & 0.444 \\
      75th percentile & 0.076 & 0.262 \\
      50th percentile & 0.066 & 0.206 \\
      25th percentile & 0.057 & 0.16 \\
      Minimum & 0.046 & 0.005 \\\hline
    \end{tabular}
    \caption{\label{tab:neuro}Summary statistics for the neuroanatomy prediction benchmarks.
    Mean absolute proportional error (MAPE) and correlation coeficient (R)
    of test-set preditions are reported accross models for all brain regions.
    Complete list of values can be found on Table S6.}
    \end{center}
\end{table}

@@

Among these, \emph{A. hadrus} is the variable with 
highest average relative importance along all reported 
(mean = 1.4\%; min = 0.8\%; max = 3.6\%, Figure 4D-E).
\emph{B. wexlerae}, which was important in RF models of cognitive function,
and was the only species to be significantly associated
with cogntive function in young children using LMs, 
was also important in models of the entorhinal, fusiform and lingual areas
and had the highest importance in models predicting the size of
both the left and right right parahippocampus.
Another cluster of model importance contained taxa associated with the
basal forebrain, especially the cingulate and the accumbens. This
cluster contains \emph{B. ovatus} and \emph{B. uniformis},
but also \emph{Alistipes finegoldii and S. salivarius}.

\emph{A. celatus}, an equol-producing species, is an examples of the second contribution
pattern, where a taxon only contributes significantly to a very small number of segments. 
This species was highly important in predicting the relative volume of
the right anterior cingulate (\hl{2.8\%} relative importance).
Another example of this pattern is \emph{Coprococcus eutactus}
which is heavily associated with the left precentral area (\hl{3.5\%} importance). 
Finally, \emph{C. comes} has an importance
distribution that splits almost evenly among the two previously reported
clusters. Its loading on the prediction of the left posterior cingulate
is the highest for a microbe in RF models (\hl{3.7\%} importance);
only age had higher relative importance in any model. At the same time,
\textit{C. comes} is one of the most important predictors for neighboring areas of the
posterior cingulate such as the pars opercularis (importances,
\hl{Left = 1.9\%, Right = 2.5\%}), along with upper regions like the left
precentral (2.0\% importance) and paracentral lobes (importances, \hl{Left = 2.0\%, Right = 1.5\%}).
